Carbonate chemistry at Ny-Ålesund

### 2021-08-24 awipev-CO2.Rmd
refine pCO2

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_fb ~ pco2_calc_fb , nperm = 99)

p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_fb, label = monthd))+
   geom_text(aes(color = factor(monthd)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```

### **Final *p*CO~2~ data**

>>>>

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Calculated vs Contros pCO2"
fit <- lmodel2(data = d_all,   pco2_calc_fb ~ pco2_fb, nperm = 99)
print(fit)
p <-  ggplot(d_all,aes(x = pco2_fb, y = pco2_calc_fb))+
  geom_point()+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  # labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
  #                    "; Intercept =", signif(fit$regression.results[2,2], 3),
  #                    "; Slope =", signif( fit$regression.results[2,3], 3),
  #                    "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()  
```

The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).

```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```

### **pCO~2~ time series**
